The Chemistry Development Kit (CDK). 3. Atom typing, Rendering, Molecular Formula, and Substructure Searching

### 2016-09-03 article.tex
Added the missing figure (closes #21)
Worked on the signatures section (closes #31)

  An implementation has been provided of the Signature structure descriptor for
  molecules~\cite{Faulon2003}. These act as a linear notation - like the SMILES format - 
  for the whole molecule as well as for connected substructures rooted at a single atom. The 
  descriptor can also be canonicalized to provide isomorphism-independent
  representations~\cite{Faulon2004}, and has been successfully used in QSAR modeling~\cite{signaturefingerprints,Spjuth2011DS,Moghadam2015,Alvarsson2014,Spjuth2012OS,Norinder2013}.

@@

\begin{verbatim}
someMolecule = fromSMILES.....
sdg.setMolecule(someMolecule);
sdg.generateCoordinates();
IAtomContainer layedOutMol = sdg.getMolecule();
\end{verbatim}

@@

%\includegraphics[width=\textwidth]{sdg2.png}

>>>>

  An implementation has been provided of the Signature structure descriptor for
  molecules~\cite{Faulon2003}. These act as a linear notation - like the SMILES format - 
  for the whole molecule as well as for connected substructures rooted at a single atom. The 
  descriptor can also be canonicalized to provide isomorphism-independent
  representations~\cite{Faulon2004}. Signatures can be calculated for atoms with:

\begin{verbatim}
\end{verbatim}

  But they can also can be calculated for full molecules:

\begin{verbatim}
\end{verbatim}

  Finally, a signatures fingerprint can be calculated for molecules, to allow
  similarity calculations. This can then be used in QSAR modeling~\cite{signaturefingerprints,
  Spjuth2011DS,Moghadam2015,Alvarsson2014,Spjuth2012OS,Norinder2013,Alvarsson2016}.
  The fingerprint for a molecule can be calculated with:

\begin{verbatim}
\end{verbatim}

@@

\begin{verbatim}
someMolecule = parser.parseSmiles("OC/C(C)=C/[C@](F)(Cl)Br");
sdg.setMolecule(someMolecule);
sdg.generateCoordinates();
IAtomContainer layedOutMol = sdg.getMolecule();
\end{verbatim}

@@

\includegraphics[width=0.3\textwidth]{sdg2.png}
